Twists of supersymmetric gauge theories

### 2020-01-08 paper.tex

We decompose the fields with respect to the subgroup $\SU(3) \sub \SO(6)$.  We can identify the two fundamental representations of $\SU(3)$ with $\Omega^{0,1}(\CC^3)$ and $\Omega^{1,0}(\CC^3)$. 
\begin{align*}
c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3) \\
\lambda & \mapsto \lambda_{0,2} w_1 + {B}_{1,0}w_2 + \chi w_1 + \lambda_0 w_2 \in \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \\
\phi & \mapsto \nu w_1 + \psi_0 w_2 \in \Omega^0(\CC^3; W_+ \otimes U) \\
\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; U) \oplus \Omega^0(\CC^3; U),
\end{align*} 
and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.  In terms of these fields, and using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory will consist of the sum of the following terms.
\begin{align*}
S_{\mr{gauge}} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
&\qquad + \frac 12 \left( \omega(\lambda_{0,2} \wedge \dd_{A_{1,0}} B_{1,0}) + \omega^2(\chi \ol \dd_{A_{0,1}} B_{1,0}) - \omega(B_{1,0} \wedge \dd_{A_{1,0}} \lambda_{0,2}) + \Omega(\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})   \right)  \\
S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \psi_0) + (\dd_{A_{1,0}}\psi_0, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2(\nu' \ol \dd_{A_{1,0}} \psi_{0,1}) + \Omega(\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \\
&\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* + [\lambda_{0,2}, A_0]\wedge \lambda_{0,2}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* + [\chi, A_0]\chi^* +A_0[B_{1,0}, A_0]\wedge B_{1,0}^* + \\
&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\nu, A_0]\wedge \nu^* + [\psi_{0}, A_0]\wedge \psi_{0}^* + [\psi_{0,1}, A_0]\wedge \psi_{0,1}^* + [\nu', A_0]\wedge \nu'^* \\
I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (B_{1,0}, A_{1,0}^*) + \frac 12 (F_{0,2},\lambda_{0,2}^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\nu', \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0, \psi_{0,1}^*) \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
\end{align*}
Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^3}6$.

>>>>

We decompose the fields with respect to the subgroup $\SU(3) \sub \SO(6)$.  We can identify the two fundamental representations of $\SU(3)$ with $\Omega^{0,1}(\CC^3)$ and $\Omega^{1,0}(\CC^3)$. 
\begin{align*}
c & \mapsto A_0 \in \Omega^{0,0}(\CC^3 ; \fg) \\
A & \mapsto A_{0,1} + A_{1,0} \in \Omega^{0,1}(\CC^3 ; \fg) \oplus \Omega^{1,0}(\CC^3) \\
\lambda & \mapsto \lambda_{0,2} w_1 + {B}_{1,0}w_2 + \chi w_1 + \lambda_0 w_2 \in \Omega^{0,2}(\CC^3 ; W_+ \otimes \fg) \oplus \Omega^{0}(\CC^3 ; W_+ \otimes \fg) \\
\phi & \mapsto \nu w_1 + \psi_0 w_2 \in \Omega^0(\CC^3; W_+ \otimes U) \\
\psi & \mapsto \psi_{0,1} + \nu' \in \Omega^{0,1}(\CC^3; U) \oplus \Omega^0(\CC^3; U),
\end{align*} 
\brian{only complaint is the use of $\psi_0$. Maybe use a different letter since $\psi$ is used for the fermion.}
and similarly with the anti-fields, where the fields $A_{\bu, \bu}$, $\lambda_{\bu,\bu}$ are $\fg$-valued differential forms, and the fields $\psi_{\bu,\bu}$ are $U$-valued differential forms.  In terms of these fields, and using Corollary \ref{Kahler_YM_term_cor}, the BV action $S_{\mr{BV}}$ of the $Q$-twisted theory will consist of the sum of the following terms.
\begin{align*}
S_{\mr{gauge}} &= \int \dvol \left(-(F^{2, 0}, F^{0, 2}) - \frac{1}{4}(\Lambda F_{1, 1})^2\right) + \\
&\qquad + \frac 12 \left( \omega(\lambda_{0,2} \wedge \dd_{A_{1,0}} B_{1,0}) + \omega^2(\chi \ol \dd_{A_{0,1}} B_{1,0}) - \omega(B_{1,0} \wedge \dd_{A_{1,0}} \lambda_{0,2}) + \Omega(\lambda_0 \ol \dd_{A_{0,1}} \lambda_{0,2})   \right)  \\
S_{\mr{matter}} &= \int \bigg( \dvol ((\dd_{A_{1,0}}\nu, \ol \dd_{A_{0,1}} \psi_0) + (\dd_{A_{1,0}}\psi_0, \ol \dd_{A_{0,1}} \nu)) + 2\omega^2(\nu' \ol \dd_{A_{1,0}} \psi_{0,1}) + \Omega(\psi_{0,1} \wedge \ol \dd_{A_{0,1}} \psi_{0,1}) + \\
&\qquad + 2\dvol(([\lambda_0,\nu],\nu') + ([\chi, \psi_0], \nu') )   \bigg) \\
S_{\mr{anti}} &= \int \dd_{A_{1, 0}} A_0 \wedge A_{1, 0}^* + \ol\dd_{A_{0, 1}} A_0\wedge A_{0, 1}^* + [\lambda_{0,2}, A_0]\wedge \lambda_{0,2}^* +  [\lambda_{0}, A_0]\wedge \lambda_{0}^* + [\chi, A_0]\chi^* +A_0[B_{1,0}, A_0]\wedge B_{1,0}^* + \\
&\qquad + \frac{1}{2}[A_0, A_0]A_0^* + [\nu, A_0]\wedge \nu^* + [\psi_{0}, A_0]\wedge \psi_{0}^* + [\psi_{0,1}, A_0]\wedge \psi_{0,1}^* + [\nu', A_0]\wedge \nu'^* \\
I^{(1)}_{\mr{gauge}} &=  \int \dvol \left( - (B_{1,0}, A_{1,0}^*) + \frac 12 (F_{0,2},\lambda_{0,2}^*) + \frac 12 (F_{1,1}, \chi^*)  \right)\\
I^{(1)}_{\mr{matter}} &=  \int \dvol \left( (\nu', \nu^*) + \frac 12( \ol \dd_{A_{0,1}} \psi_0, \psi_{0,1}^*) \right)\\
I^{(2)}_{\mr{gauge}} &= -\frac{1}{4}\int \dvol (\chi^*)^2.
\end{align*}
Here, in terms of the K\"ahler form $\omega$, the volume form is identified as $\dvol = \frac{\omega^3}6$.
